Equivalent Income Stuff - Energy Crisis Plots

### 2024-01-05 minos/outcomes/EI_allScen_Plots.Rmd
Amelia still WIP. Added script for visualising various things from interventions in Equivalent Income terms

```{r}
# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
# out.path.batch <- here::here('output', 'SIPHER7_batch/')
# 
# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')

@@

```{r}
## second batch dump
out.path.arc2 <- here::here('output', 'batch')

#target.pattern <- paste0('aggregated_run_id_', year, '.csv')
base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
                            full.names = TRUE)
base.batch <- do.call(rbind, lapply(base.list, read.csv))

energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
                            full.names = TRUE)
energy.batch <- do.call(rbind, lapply(energy.list, read.csv))

int.name <- 'Energy Crisis'
```

@@

base.batch <- calc_age_group(base.batch)
energy.batch <- calc_age_group(energy.batch)
```

@@

base.batch <- calc_income_quintile(base.batch)
energy.batch <- calc_income_quintile(energy.batch)
```

@@

```{r}
income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
```

@@

```{r}
inc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
```

>>>>

```{r}
S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
out.path.batch <- here::here('output', 'SIPHER7_batch/')

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

#out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')

@@

```{r}
## second batch dump
# out.path.arc2 <- here::here('output', 'batch')
# 
# #target.pattern <- paste0('aggregated_run_id_', year, '.csv')
# base.list <- list.files(path = paste0(out.path.arc2, '/baseline'),
#                             full.names = TRUE)
# base.batch <- do.call(rbind, lapply(base.list, read.csv))
# 
# energy.list <- list.files(path = paste0(out.path.arc2, '/energy'),
#                             full.names = TRUE)
# energy.batch <- do.call(rbind, lapply(energy.list, read.csv))

#base.batch <- 
```

@@

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
energy.batch <- calc_age_group(energy.batch)
child.batch <- calc_age_group(child.batch)
pov.batch <- calc_age_group(pov.batch)
```

@@

base.batch <- calc_income_quintile(base.batch)
wage.batch <- calc_income_quintile(wage.batch)
energy.batch <- calc_income_quintile(energy.batch)
child.batch <- calc_income_quintile(child.batch)
pov.batch <- calc_income_quintile(pov.batch)
```

@@

```{r}
income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_change_batch(base.batch, child.batch, 'All Child Uplift')
income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child Uplift')
```

@@

```{r}
inc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')

inc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')

inc_change_batch_subpop(base.batch, child.batch, 'All Child Uplift', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, child.batch, 'All Child Uplift', group.var = 'income.quint')

inc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child Uplift', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child Uplift', group.var = 'income.quint')
```
